Indirect climate effects on biomass partitioning

### 2014-11-18 manuscript/draftpaper.Rnw
added some author instructions, changed title
New figure SI-9, using MI and mgdd0.

\title{A global compilation reveals divergent biomass partitioning between plant functional types }

@@

@@

% \section{flow}
% 
% \begin{itemize}
% 
% \item First paragraph
% \item Allocation in models, main uncertainties
% \item Climate effects on partioning : direct (MAT, MAP), indirect (PFT).
% \item Known: gymnosperm vs. angiosperm. Unknown: leaf habit (deciduous vs. evergreen), direct climate, patterns for individual plants
% \item BAAD : Largest database, other large datasets are stands or only small plants
% \item Root scaling no PFT differences, focus on aboveground
% \item LMF, LAR
% \item Found very large LMF differences, but convergent LAR
% \item decompose into MF/AS, MT/AS, find similar differences in MF/AS but none in MT/AS, suggesting convergent AF/AS between PFTs.
% \item No direct climate effects, so shift in PFT captures global patterns in biomass partioning
% \item This has implications for allocation in DGVMs, they can be divided into roughly three categories in terms of biomass allocation (allocation fractions, allometric constraints, LAI optimization). Allocation vs. partitioning: the role of leaf and stem turnover.
% 
% \end{itemize}

@@

Unlike \cite{reich_temperature_2014}, we found only very weak effects of mean annual temperature the scaling of leaf biomass with woody biomass (Fig.~\ref{fig:figureSI9}). The variance explained by MAT was very small, especially compared to the large difference between PFTs. These results were confirmed with a mixed-effects model of MF vs. MS, with MAT and PFT as covariates (see Table~\ref{table:matlmeanova}). We found no significant effects of mean annual precipitation of leaf-woody biomass relationships (Table~\ref{table:maplmeanova}).

@@

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{FigureSI-9_MAT_LMFscaling.pdf}
    \caption{For each species within study, we fit the scaling relationship of leaf mass as a function of woody biomass assuming an exponent of 3/4, using standardized major axis. The resulting coefficient (b0) is size-invariant (and thus superior to the simple ratio of leaf mass to woody biomass, which is strongly size-dependent, see Fig.~\ref{fig:figure3}). We found no effects of mean annual temperature on the coefficient. The triangles are from Roth et al. (2007), a study on Pinus eliottii with exceptionally high leaf mass per unit woody biomass.}
  \label{fig:figureSI9}
\end{figure}

>>>>

\title{Indirect climate effects on biomass partitioning}

@@

% First paragraph The first paragraph should be 180 to 200 words and should contain references. The paragraph should serve both as a general introduction to the topic and as a brief, non-technical summary of your main results and their implications. Ideally, the paragraph starts with two to three sentences of background explaining the topic and current understanding. This is followed by a phrase like “Here we present” to introduce the new work. In the second part, the main methods, findings, conclusions and implications should be described clearly and accessibly.

@@

% \section{flow}
% 
% \begin{itemize}
% 
% \item First paragraph
% \item Allocation in models, main uncertainties
% \item Climate effects on partioning : direct (MAT, MAP), indirect (PFT).
% \item Known: gymnosperm vs. angiosperm. Unknown: leaf habit (deciduous vs. evergreen), direct climate, patterns for individual plants.
% \item BAAD : Largest database, other large datasets are stands or only small plants
% \item Root scaling no PFT and very weak climate differences, focus on aboveground
% \item Found very large LMF differences, but convergent LAR
% \item decompose into MF/AS, MT/AS, find similar differences in MF/AS but none in MT/AS, suggesting convergent AF/AS between PFTs.
% \item Only small direct climate effects, so shift in PFT captures global patterns in biomass partioning.
% \item This has implications for allocation in DGVMs, they can be divided into roughly three categories in terms of biomass allocation (allocation fractions, allometric constraints, LAI optimization). Allocation vs. partitioning: the role of leaf and stem turnover.
% 
% \end{itemize}

@@

Unlike \cite{reich_temperature_2014}, we found only very weak effects of climate on biomass relationships. The variance explained by MAT was very small, especially compared to the large difference between PFTs. These results were confirmed with a mixed-effects model of MF vs. MS, with MAT and PFT as covariates (see Table~\ref{table:matlmeanova}). We found no significant effects of mean annual precipitation of leaf-woody biomass relationships (Table~\ref{table:maplmeanova}).

@@

% Figures A Nature Climate Change Letter can contain up to four display items (any combination of figures and/or tables). Figures should be sized in single or double column format. Multi-panel figures should be arranged so that the figure forms a neat rectangle.

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.99\textwidth]{FigureSI-9_climateeffects.pdf}
    \caption{Modest effects of climate on three size-invariant variables, compared to the very large effect of plant functional type on mass-based variables (leaf mass per area, LMA, and $M_F/A_S$), and convergence in area-based variables ($A_F/A_S$). See SI Methods for calculation of MI and growing season temperature. Solid lines are generalized additive model fits (with a base dimension of 3, larger values resulted in biologically implausible relationships). Grey areas are approximate 95\% confidence intervals, calculated by the gam after averaging each variable by species/dataset combination (but all raw individual plant data are shown in the plots).}
  \label{fig:figureSI9}
\end{figure}
